Flexibility reduces social donations

### 2021-11-16 article-elsevier/article-elsevier.Rmd
intento formato gráficos

---
title: Flexibility reduces social donations
author:
  - name: Sebastián Cea-Echenique
    email: sebastian.cea@pucv.cl
    affiliation: School of Industrial Engineering, Pontificia Universidad Católica de Valparaíso
    footnote: 1
  - name: Claudia Toledo-Aguirre
    email: claudia.toledo@pucv.cl
    affiliation: School of Industrial Engineering, Pontificia Universidad Católica de Valparaíso
#   - name: Cat Memes
#     email: cat@example.com
#     affiliation: Another University
#     footnote: 2
#   - name: Derek Zoolander
#     email: derek@example.com
#     affiliation: Some Institute of Technology
#     footnote: 2
# address:
#   - code: Some Institute of Technology
#     address: Department, Street, City, State, Zip
#   - code: Another University
#     address: Department, Street, City, State, Zip
footnote:
  - code: 1
    text: "Corresponding Author"
  # - code: 2
    # text: "Equal contribution"
abstract: |
  We exploit a change in tax donations' law to evaluate a change to more flexibility.

@@

load("~/workspace/donationstax/data_local/Donaciones_total_graficos.Rdata")
load("~/workspace/donationstax/data_local/Datos_seleccion_modelo.Rdata")
knitr::opts_chunk$set(fig.width=5, fig.height=5)

@@

```{r graficos_donaciones_1, echo = FALSE,message=FALSE,warning = FALSE, fig.align="center",dev='png',dpi=200}
#grafico con donaciones y cambio de leyes
ggplot(Donaciones_total, aes(x = Fecha , y = monto_total_UTM)) +
  # Make points small and semi-transparent since there are lots of them
  geom_point(size = 0.5, alpha = 0.5) + 
  # Add vertical line
  #geom_hline(yintercept=1000, linetype="dashed", color = "red") +
  geom_vline(xintercept=as.numeric(as.Date("2010-01-01")), linetype="dashed", color = "red") +
  geom_vline(xintercept=as.numeric(as.Date("2011-01-01")), linetype="dashed", color = "red") +
  geom_vline(xintercept=as.numeric(as.Date("2012-02-08")), linetype="dashed", color = "red") +
  geom_vline(xintercept=as.numeric(as.Date("2016-04-14")), linetype="dashed", color = "red") +
  # Add labels
  labs(x = "Date", y = "Total donation")+
  ylim(0,20000)+
  xlim(as.Date("2008-01-01"),as.Date("2018-12-31"))+
  annotate("text", x = as.Date("2008-09-11"), y = 19500, label = "Law 19885")+
  annotate("text", x = as.Date("2010-01-01"), y = 18000, label = "Law 20316")+
  annotate("text", x = as.Date("2011-01-01"), y = 20000, label = "Law 20565")+
  annotate("text", x = as.Date("2012-04-08"), y = 16000, label = "Law 20900_1")+
  annotate("text", x = as.Date("2016-04-14"), y = 19000, label = "Law 20900_2")+
  ggtitle("Donations: Total amount over time")

@@

```{r graficos_donaciones_2, echo = FALSE,message=FALSE,warning = FALSE, fig.align="center",dev='png',dpi=200}

@@

```{r graficos_donaciones_3, echo = FALSE,message=FALSE,warning = FALSE, fig.align="center",dev='png',dpi=200}
ggplot(Donaciones_total, aes(x = Fecha , y = monto_FM_UTM)) +
  # Make points small and semi-transparent since there are lots of them
  geom_point(size = 0.5, alpha = 0.5) + 
  # Add vertical line
  #geom_hline(yintercept=1000, linetype="dashed", color = "red") +
  geom_vline(xintercept=as.numeric(as.Date("2010-01-01")), linetype="dashed", color = "red") +
  geom_vline(xintercept=as.numeric(as.Date("2011-01-01")), linetype="dashed", color = "red") +
  geom_vline(xintercept=as.numeric(as.Date("2012-02-08")), linetype="dashed", color = "red") +
  geom_vline(xintercept=as.numeric(as.Date("2016-04-14")), linetype="dashed", color = "red") +
  # Add labels
  labs(x = "Date", y = "Donation to Mixed Found")+
  ylim(0,2500)+
  xlim(as.Date("2008-01-01"),as.Date("2018-12-31"))+
  annotate("text", x = as.Date("2008-09-11"), y = 2500, label = "Law 19885")+
  annotate("text", x = as.Date("2009-11-01"), y = 2000, label = "Law 20316")+
  annotate("text", x = as.Date("2011-01-01"), y = 2200, label = "Law 20565")+
  annotate("text", x = as.Date("2012-04-08"), y = 1850, label = "Law 20900_1")+
  annotate("text", x = as.Date("2016-04-14"), y = 2000, label = "Law 20900_2")+
  ggtitle("Donations: Mixed Found amount over time")

>>>>

---
title: Flexibility reduces social donations
author:
  - name: Sebastián Cea-Echenique
    email: sebastian.cea@pucv.cl
    affiliation: School of Industrial Engineering, Pontificia Universidad Católica de Valparaíso
    footnote: 1
  # - name: Claudia Toledo-Aguirre
  #   email: claudia.toledo@pucv.cl
  #   affiliation: School of Industrial Engineering, Pontificia Universidad Católica de Valparaíso
#   - name: Cat Memes
#     email: cat@example.com
#     affiliation: Another University
#     footnote: 2
#   - name: Derek Zoolander
#     email: derek@example.com
#     affiliation: Some Institute of Technology
#     footnote: 2
# address:
#   - code: Some Institute of Technology
#     address: Department, Street, City, State, Zip
#   - code: Another University
#     address: Department, Street, City, State, Zip
footnote:
  - code: 1
    text: "Corresponding Author"
  # - code: 2
    # text: "Equal contribution"
abstract: |
  We exploit a change in tax donations' law to evaluate a change to more flexibility.

@@

load("../data_local/Donaciones_total_graficos.Rdata")
load("../data_local/Datos_seleccion_modelo.Rdata")
knitr::opts_chunk$set(fig.width=5, fig.height=5)

@@

```{r graficos_donaciones_1, echo = FALSE,message=FALSE,warning = FALSE, fig.align="center", out.width="40%"}
#grafico con donaciones y cambio de leyes
ggplot(Donaciones_total, aes(x = Fecha , y = monto_total_UTM)) +
  # Make points small and semi-transparent since there are lots of them
  geom_point(size = 0.5, alpha = 0.5) + 
  # Add vertical line
  #geom_hline(yintercept=1000, linetype="dashed", color = "red") +
  geom_vline(xintercept=as.numeric(as.Date("2010-01-01")), linetype="dashed", color = "red") +
  geom_vline(xintercept=as.numeric(as.Date("2011-01-01")), linetype="dashed", color = "red") +
  geom_vline(xintercept=as.numeric(as.Date("2012-02-08")), linetype="dashed", color = "red") +
  geom_vline(xintercept=as.numeric(as.Date("2016-04-14")), linetype="dashed", color = "red") +
  # Add labels
  labs(x = "Date", y = "Total donation")+
  ylim(0,20000)+
  xlim(as.Date("2008-01-01"),as.Date("2018-12-31"))+
  annotate("text", x = as.Date("2008-09-11"), y = 19500, label = "Law 19885")+
  annotate("text", x = as.Date("2010-01-01"), y = 18000, label = "Law 20316")+
  annotate("text", x = as.Date("2011-01-01"), y = 20000, label = "Law 20565")+
  annotate("text", x = as.Date("2012-04-08"), y = 16000, label = "Law 20900_1")+
  annotate("text", x = as.Date("2016-04-14"), y = 19000, label = "Law 20900_2")+
  ggtitle("Donations: Total amount over time")

@@

```{r graficos_donaciones_2, echo = FALSE,message=FALSE,warning = FALSE, fig.align="center", out.width="40%"}

@@

```{r graficos_donaciones_3, echo=FALSE, fig.align="center", message=FALSE, warning=FALSE, out.width="20%"}
ggplot(Donaciones_total, aes(x = Fecha , y = monto_FM_UTM)) +
  # Make points small and semi-transparent since there are lots of them
  geom_point(size = 0.5, alpha = 0.5) + 
  # Add vertical line
  #geom_hline(yintercept=1000, linetype="dashed", color = "red") +
  geom_vline(xintercept=as.numeric(as.Date("2010-01-01")), linetype="dashed", color = "red") +
  geom_vline(xintercept=as.numeric(as.Date("2011-01-01")), linetype="dashed", color = "red") +
  geom_vline(xintercept=as.numeric(as.Date("2012-02-08")), linetype="dashed", color = "red") +
  geom_vline(xintercept=as.numeric(as.Date("2016-04-14")), linetype="dashed", color = "red") +
  # Add labels
  labs(x = "Date", y = "Donation to Mixed Fund")+
  ylim(0,2500)+
  xlim(as.Date("2008-01-01"),as.Date("2018-12-31"))+
  annotate("text", x = as.Date("2008-09-11"), y = 2500, label = "Law 19885")+
  annotate("text", x = as.Date("2009-11-01"), y = 2000, label = "Law 20316")+
  annotate("text", x = as.Date("2011-01-01"), y = 2200, label = "Law 20565")+
  annotate("text", x = as.Date("2012-04-08"), y = 1850, label = "Law 20900_1")+
  annotate("text", x = as.Date("2016-04-14"), y = 2000, label = "Law 20900_2")+
  ggtitle("Donations: Mixed Found amount over time")
